Functional timeseries reveal no systemic shifts in vertebrate communities

### 2021-07-21 paper/manuscript.Rmd
small comment

Trends in functional composition also have important implications for how we assesses potential changes in ecosystem stability, function, and resilience.
Functional loss is often implicit in work linking biodiversity loss to impacts on ecosystem processes despite a wide range of documented relationships between functional and species change in natural communities [@biswas2011].
<!-- For example, hypotheses underpining the biodiversity ecosystem function relationship: insert function/stability theory here. --> Where functional diversity is explicitly considered, there is increasing evidence it is a better predictor of ecosystem function than species-based metrics [@cadotte2011; @gagic2015], and that different facets of functional diversity play essential roles in maintaining ecosystem stability [@craven2018; @morin2014].
Tracking the relationship between species and functional changes across a wide variety of communities therefore provides an opportunity to assess not only the prevalence of concurrent species and functional loss, but also the evidence underpinning hypothesis between biodiversity loss and ecosystem processes.

@@

>>>>

Beyond simply characterizing changes in community structure, trends in functional composition also have important implications for ecosystem stability, function, and resilience.
There is increasing evidence functional diversity is a better predictor of ecosystem function than species-based metrics [@cadotte2011; @gagic2015], and that different facets of functional diversity play essential roles in maintaining ecosystem stability [@craven2018; @morin2014]. Indeed, almost all hypothesized mechanisms underpinning the relationship between species diversity and ecosystem function are trait-dependent [@hillebrand2009]. Determining functional trends therefore gives a more complete picture of potential trends in critical ecosystem processes.

While functional loss is frequently cited as one of the most pressing concerns of the anthropocene (CITATIONS), observed and projected functional diversity trends are less certain.
Forecasts of functional loss range from negligible [@gallagher2013] to dire [@petchey2002; @pimiento2020]. And while some observed trends show significant functional loss [@flynn2009] others document no loss even in some of the most heavily impacted communities [@matuoka2020]. Overall trends are therefore necessary... Clearly functional loss is not inevitable in scenarios of perturbation or even species loss [@daz2001].

<!-- trends in functional composition also have important implications for how we assesses potential changes in ecosystem stability, function, and resilience. Functional loss is often implicit in work linking biodiversity loss to impacts on ecosystem processes despite a wide range of documented relationships between functional and species change in natural communities [@biswas2011]. Where functional diversity is explicitly considered, there is increasing evidence it is a better predictor of ecosystem function than species-based metrics [@cadotte2011; @gagic2015], and that different facets of functional diversity play essential roles in maintaining ecosystem stability [@craven2018; @morin2014]. Tracking the relationship between species and functional changes across a wide variety of communities therefore provides an opportunity to assess not only the prevalence of concurrent species and functional loss, but also the evidence underpinning hypothesis between biodiversity loss and ecosystem processes. -->

@@

<!-- description of edge case where community = species pool -->
